Multi-product Batch Processing Time Maximization Problem

### 2023-07-05 (2023) Fraga et al.tex
updating files

\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}

\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
             city={Caruaru},
             postcode={55014-900},
             state={PE},
             country={Brasil}}

>>>>

%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}

%\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
%             city={Caruaru},
%             postcode={55014-900},
%             state={PE},
%             country={Brasil}}
